Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations

### 2016-02-11 doc/manuscript.tex
new version of figure

\title{Extracellular potentials generated by axonal projections are shaped by
patterns of bifurcations and terminations}
\author{Thomas McColgan, Hermann Wagner, Richard Kempter}
\date{\today}

@@

It is interesting to note that a similar reversal of polarity in NL has
been reported for chicken (Schwarz, 1992), as well as in the mamalian
analog to NL, the medial superior olive (Laughlin et al., 2010). The
phase reversal in this case has been modeled based on the assumption
that the postsynaptic NL and MSO dendrites with their bipolar morphology
have a dipolar EFP response (Laughlin et al., 2010; Goldwyn et al.,
2014). However, in the owl this dipolar morphology is largely absent
(Carr and Konishi, 1990), making dendritic sources unlikely.

>>>>

\title{Extracellular potentials generated by axonal projections are shaped by
patterns of bifurcations and terminations}
\author{Thomas McColgan, Hermann Wagner, Richard Kempter}
\date{\today}
\usepackage{setspace}
\doublespacing

@@

It is interesting to note that a similar reversal of polarity in NL has
been reported for chicken (Schwarz, 1992), as well as in the mammalian
analog to NL, the medial superior olive (Laughlin et al., 2010). The
phase reversal in this case has been modeled based on the assumption
that the postsynaptic NL and MSO dendrites with their bipolar morphology
have a dipolar EFP response (Laughlin et al., 2010; Goldwyn et al.,
2014). However, in the owl this dipolar morphology is largely absent
(Carr and Konishi, 1990), making dendritic sources unlikely.
